Title

### 2015-12-10 paper/paper.tex
status commit before rearranging sections

As noted in Related Work, our ordering model does not require the number of
sentences to be fixed to a particular value. If it were to impose such a
requirement, then the subgraph selection, which is further upstream in our
pipeline, may not be able to find its optimal partitioning simply because it
was a partitioning into a different number of sentences. As a result, our model
could not rely on any features that deal with particular sentences (e.g. the
similarity between the second and fifth sentences). So, we tried to use
features that would generalize to paragraphs of any length, but would still
vary with the ordering of those sentences within the paragraph, and all
features had to be summarized (mean, standard deviation, min, max) over the
paragraph. Features included the Jaccard similarity between adjancent
sentences, between sentences that are two sentences apart, and the Jaccard
similarity between the union of adjacent sentences and the overall paragraph.

>>>>

As noted in Related Work, our ordering model does not require the number of
sentences to be fixed to a particular value. If it were to impose such a
requirement, then the subgraph selection, which is further upstream in our
pipeline, may not be able to find its optimal partitioning simply because it
was a partitioning into a different number of sentences. As a result, our model
could not rely on any features that deal with particular sentences (e.g. the
similarity between the second and fifth sentences). So, we tried to use
features that would generalize to paragraphs of any length, but would still
vary with the ordering of those sentences within the paragraph, and all
features had to be summarized (mean, standard deviation, min, max) over the
paragraph. Features included the Jaccard similarity between adjancent
sentences, between sentences that are two sentences apart, and the Jaccard
similarity between the union of adjacent sentences and the overall paragraph.
The following table summarizes the features used for subgraph ordering:

\begin{table}
\centering
\begin{tabular}{|r|c|c|}
\hline
Feature & \\ \hline\hline
Pairwise Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+1}$ \\ \hline
Two-apart Jaccard & Jaccard similarity of the AMR graphs for sentences $s_i,s_{i+2}$ \\ \hline
Pairwise node Jaccard & Jaccard similarity of just the vertex sets for sentences $s_i,s_{i+1}$ \\ \hline
Comibined Jaccard & Jaccard similarity between the paragraph AMR and $s_i \cup
s_{i+1}$ \\ \hline
\end{tabular}
\caption{Subgraph Ordering Features}
\end{table}
